---
title: "Trains"
author: "Var Kurapati"
format: html
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(gt)
library(marginaleffects)
```

```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |> fit(att_end ~ treatment, data = trains)
```

```{r}
plot_predictions(fit_att, condition = "treatment", draw = FALSE) |>
  ggplot(aes(x = treatment, y = estimate, color = treatment)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  labs(
    title = "Causal Effect of Spanish-Speaker Exposure on Immigration Attitudes",
    subtitle = "Treated commuters show higher anti-immigration attitudes than controls",
    x = "Treatment Group",
    y = "Predicted Attitude Score (3-15 scale)",
    color = "Treatment",
    caption = "Source: Enos (2014) via primer.data::trains"
  )
```

Attitudes toward immigration respond to brief encounters with speakers 
of another language, at least in the short run. Using data from Ryan 
Enos's January 2012 randomized experiment on Boston-area Metra platforms 
(115 commuters, randomly assigned to exposure or non-exposure to 
Spanish-speaking confederates for two weeks), we estimate the average 
causal effect of that exposure on anti-immigration attitudes. However, 
since the experiment was conducted exclusively on Boston commuter 
platforms in 2012, the estimated effect may not generalize to other 
cities or the current political climate, where attitudes toward 
immigration have shifted considerably. We model att_end, immigration 
attitude scores measured after the experiment, as a linear function of 
treatment, the randomized exposure to Spanish-speaking confederates. We 
estimate that exposure to Spanish-speaking confederates increases 
anti-immigration attitude scores by about 1.55 points on the 3–15 scale 
(95% CI: 0.51–2.58), suggesting that even brief everyday contact can 
shift attitudes toward immigration in the short run.

Our estimates are likely too narrow in scope because the experiment was 
conducted on a small, self-selected sample of 115 Boston commuters in 
January 2012, a single city and time period that may not represent how 
other populations would respond to similar exposure today. While 
randomization should ensure unconfoundedness within this sample, the 
validity of treating the experiment's narrow definition of 'exposure' 
as representative of everyday encounters with Spanish-speakers elsewhere 
is uncertain, and the political climate around immigration has shifted 
substantially since 2012 in ways that could change the size or even 
direction of this effect. The confidence interval also only captures 
sampling uncertainty within this experiment, not the broader uncertainty 
about whether this effect would replicate in a different setting.




