---
title: "Trains"
author: "Var Kurapati"
format: html
execute:
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
```

```{r}
trains |>
  ggplot(aes(x = treatment, y = att_end, color = treatment)) +
  geom_jitter(width = 0.2, alpha = 0.6) +
  stat_summary(fun = mean, geom = "point", size = 4, shape = 18, color = "black") +
  labs(
    title = "Post-Experiment Immigration Attitudes by Treatment Group",
    subtitle = "Black diamonds show group means; treated commuters score slightly higher",
    x = "Treatment",
    y = "Attitude Score (higher = more anti-immigration)",
    color = "Treatment",
    caption = "Source: Enos (2014) via primer.data::trains"
  )
```

```{r}
glimpse(trains)
```

Attitudes toward immigration respond to brief encounters with speakers 
of another language, at least in the short run. Using data from Ryan 
Enos's January 2012 randomized experiment on Boston-area Metra platforms 
(115 commuters, randomly assigned to exposure or non-exposure to 
Spanish-speaking confederates for two weeks), we estimate the average 
causal effect of that exposure on anti-immigration attitudes. However, 
since the experiment was conducted exclusively on Boston commuter 
platforms in 2012, the estimated effect may not generalize to other 
cities or the current political climate, where attitudes toward 
immigration have shifted considerably.

